\chapter{Lean and Mathlib}
\label{chap:introduction}

The practice of mathematics is fundamentally rooted in the rigorous verification of proofs.
However, as mathematical theories grow increasingly complex, the traditional peer-review process
becomes strained. The digitization and formal verification of mathematics offer a modern solution
to this problem, allowing mathematicians to verify their results with absolute certainty using
software.

This chapter introduces the Lean theorem prover and the mathematics library in the software
system called \lstinline|Mathlib|.

\section{The Lean Theorem Prover}
\label{sec:lean_theorem_prover}

Lean is a functional programming language and interactive theorem prover initially developed
by Leonardo de Moura at Microsoft Research in 2013 \cite{demoura2015lean}. The current version, Lean 4,
is a complete reimplementation that serves simultaneously as a proof assistant and a
general-purpose, practically efficient programming language.

At its logical core, Lean is based on a variant of dependent type theory known as the
Calculus of Inductive Constructions (CIC). In this framework, propositions are represented
as types, and proofs are represented as terms of those types—a correspondence known as the
Curry-Howard isomorphism.

To prove a theorem in Lean is to construct a term of the corresponding type. Lean's kernel,
a small and highly trusted piece of code, checks that this term is well-typed. If the kernel
accepts the term, the proof is logically sound. This minimizes the trusted code base; users
do not need to trust the complex tactics or automation used to generate the proof, only the
kernel that verifies the final proof term.

% Unlike traditional computer algebra systems (such as Mathematica or SageMath) which
% primarily perform numerical and symbolic computations, interactive theorem provers
% like Lean are designed to reason about abstract mathematical concepts, properties, and
% logical deductions.

\section{Dependent Type Theory}
\label{sec:dependent_type_theory}

Traditional set theory (such as Zermelo-Fraenkel with Choice, ZFC) has historically served
as the foundation of mathematics. However, dependent type theory provides a more natural
environment for machine verification.

In Lean's type theory, every expression has a specific type. The defining feature of
\textit{dependent} type theory is that types can depend on terms. For example,
the type of a vector of length $n$, denoted \lstinline|Vector a n|, depends on the natural
number $n$. This allows for highly expressive typing where the properties of mathematical
objects are baked directly into their definitions.

% Lean distinguishes between two fundamental universes:
% \begin{itemize}
%     \item \texttt{Prop}: The universe of logical propositions. Types residing in \texttt{Prop} are
%     subject to proof irrelevance, meaning any two proofs of the same proposition are considered
%     definitionally equal.
%     \item \texttt{Type}: The universe of data and mathematical structures
%     (e.g., natural numbers, rings, manifolds).
% \end{itemize}

Moreover, even types themselves have types. The type of propositions \lstinline|Prop| is also
of type \lstinline|Type|. As to not run into a paradox called Girard's paradox there is a hierarchy of
types in \cite{Coquand1986}.
The type of \lstinline|Type| is \lstinline|Type 1|, the type of \lstinline|Type 1|
is \lstinline|Type 2| and so on. These are call type-universe. We can also say \lstinline|R| is a
type in an arbitrary univer and we denote it as \lstinline|R : Type*|.

\section{Inductive type and Quotient type}

\subsection{Inductive type}

In the Lean proving system, the vast majority of mathematical objects, data structures, and
logical propositions are defined as \textit{inductive types}.

An inductive type is defined by specifying its universe level and a comprehensive list of its
\textit{constructors}. Mathematically, inductive types are ``freely generated''
by these constructors. Here are several examples in Mathlib

\begin{lstlisting}
inductive Nat where
  | zero : Nat
  | succ (n : Nat) : Nat

inductive List (α : Type u) where
  | nil : List α
  | cons (head : α) (tail : List α) : List α

inductive Option (α : Type u) where
  /-- No value. -/
  | none : Option α
  /-- Some value of type `α`. -/
  | some (val : α) : Option α
\end{lstlisting}

In the inductive construction of \lstinline|List|, \lstinline|nil| means the empty list,
usually written \lstinline|[]|. And the inductive construction of \lstinline|List| is that:
the list whose first element is \lstinline|head|, where \lstinline|tail| is the rest of the list.
Usually written \lstinline|head :: tail|.

Because inductive types are freely generated, Lean automatically enforces two strict rules, often
referred to as the ``no confusion'' properties \cite{deMoura2021}:
\begin{enumerate}
    \item Injectivity of Constructors: If $\texttt{succ}(a) = \texttt{succ}(b)$, then $a = b$.
    \item Disjointness of Constructors: Different constructors can never produce the same value.
    For example, $\texttt{zero} \neq \texttt{succ}(a)$ for any $a$.
\end{enumerate}

These properties are what allow functions to be defined via pattern matching and recursive
evaluation. Is each type in Lean an inductive type? The answer is almost but not.
Every type in Lean is either an inductive type, or defined in terms of
universes (like the type \lstinline|Type 2|), functions and quotient types.

\subsection{Quotient types}
In abstract algebra and topology, it is frequently necessary to construct a new
space by ``gluing'' elements of a base space together according to an equivalence relation $\sim$.

If one were to attempt to define a quotient type as a standard inductive type, they would
face a contradiction. One might try to provide a constructor
$\texttt{mk} : \alpha \to \text{Quotient}$, but because inductive constructors are strictly
injective, Lean would enforce that if $a \neq b$, then $\texttt{mk}(a) \neq \texttt{mk}(b)$.
This entirely defeats the purpose of a quotient, where we explicitly want
$\texttt{mk}(a) = \texttt{mk}(b)$ whenever $a \sim b$.

To resolve this, Lean does not treat quotients as inductive types.
Instead, it extends its core type theory with a set of primitive axioms
specifically designed for quotienting \cite{Carneiro2019}.

Lean introduces four foundational constants to handle quotients for any type
$\alpha$ and relation $r : \alpha \to \alpha \to \texttt{Prop}$:

\begin{enumerate}
    \item \lstinline|Quot| is the built-in quotient type.
    \item \lstinline|Quot.mk| places elements of the underlying type \lstinline|α| into the quotient.
    \item \lstinline|Quot.lift| allows the definition of functions from the quotient to some other type.
    \item \lstinline|Quot.ind| is used to write proofs about quotients by assuming that all elements are constructed
        with \lstinline|Quot.mk|.
\end{enumerate}

\begin{lstlisting}
axiom Quot.sound : ∀ {α : Sort u} {r : α → α → Prop} {a b : α},
    r a b → Quot.mk r a = Quot.mk r b
\end{lstlisting}

By utilizing \texttt{Quot.sound}, Lean intentionally breaks the injectivity rule that governs inductive types, allowing for true mathematical equivalence classes. Functions out of quotient types are then defined using \texttt{Quot.lift}, which requires the user to provide a proof that the function respects the underlying equivalence relation (i.e., the function is well-defined).

% \section{Mathlib: The Mathematical Library}
% \label{sec:mathlib}

% The power of an interactive theorem prover depends heavily on the extent of its standard library. For Lean, this is \textsf{mathlib}, a massive, community-driven repository of formalized mathematics.

% Unlike other theorem provers that often split theories into disconnected libraries, \textsf{mathlib} is heavily integrated and monolithic. This design choice ensures that different areas of mathematics can interact seamlessly. A theorem proven in topology can be immediately applied to algebraic geometry without needing to bridge incompatible definitions of fundamental structures.

% \textsf{mathlib} covers a vast array of topics, including but not limited to:
% \begin{itemize}
%     \item Abstract algebra (groups, rings, modules, category theory)
%     \item Analysis (topology, measure theory, functional analysis)
%     \item Geometry (manifolds, schemes)
%     \item Combinatorics and number theory
% \end{itemize}

% Furthermore, \textsf{mathlib} relies heavily on Lean's typeclass inference system. This system allows Lean to automatically synthesize required mathematical structures—for instance, automatically deducing that the product of two topological spaces is a topological space, or identifying the correct multiplicative inverse operation for an element in a ring.

% By building upon the rigorous foundations of Lean 4 and the extensive mathematical scaffolding of \textsf{mathlib}, this thesis contributes to the ongoing effort to digitize modern mathematics.

\section{Structures, Classes, and Type Class Inference}
\label{sec:structures_classes_inference}

To effectively formalize mathematics, a system must be able to organize abstract concepts—such
as groups, rings, and topological spaces—in a modular and extensible way. Lean achieves this
using structures and type classes.

\subsection{Structures and Classes}
In Lean, a \lstinline|structure| is an inductive type with a single constructor, akin to a record
in traditional programming languages. It allows users to bundle data (such as mathematical
operations) and propositions (such as axioms) into a single cohesive object. For example,
a group can be defined as a structure containing a carrier type, a multiplication operation,
an identity element, an inverse operation, and the explicit proofs that these operations
satisfy the standard group axioms.

A \lstinline|class| is simply a \lstinline|structure| that has been registered with Lean's type
class resolution system. In mathematical formalization, we almost exclusively use classes
to define algebraic and topological properties. By doing so, we define generic interfaces
that many different specific types (e.g., the integers, polynomials, or matrices) can instantiate.

\subsection{Type Class Inference}
Type class inference is the automated mechanism by which Lean synthesizes missing
mathematical context. When a theorem or definition requires an instance of a class—denoted by
square brackets in Lean's syntax, such as \lstinline|[Ring R]|—Lean searches its
environment to automatically construct and inject the required instance.

This system is the absolute backbone of mathematical notation and generic reasoning in Lean.
For instance, the addition symbol \lstinline|+| is defined via a fundamental type class called
\lstinline|Add|. When Lean encounters the expression \lstinline|a + b| for variables
\lstinline|a b : R|, it implicitly triggers type class inference to find an instance of
\lstinline|Add R|. If \lstinline|R| is known to be a ring via a local assumption,
Lean seamlessly infers the correct addition operation without the user needing to
manually specify it. This mechanism allows formalized mathematics to remain readable
and closely resemble traditional pen-and-paper mathematics.

\subsection{The Algebraic Hierarchy}
In \textsf{mathlib}, mathematical structures are organized into a massive, heavily intertwined
algebraic hierarchy. This hierarchy is built using class extension.
\begin{lstlisting}
class Semiring (α : Type u) extends NonUnitalSemiring α, NonAssocSemiring α, MonoidWithZero α

class Ring (R : Type u) extends Semiring R, AddCommGroup R, AddGroupWithOne R

class CommRing (α : Type u) extends Ring α, CommMonoid α
\end{lstlisting}

For instance,
the \lstinline|CommRing| (commutative ring) class extends the \lstinline|Ring| class, which in
turn extends both \lstinline|Semiring|, \lstinline|AddCommGroup| and \lstinline|AddGroupWithOne|,
cascading all the way down to basic operational classes like \lstinline|Mul| and \lstinline|Add|.

Because of this hierarchy, a theorem proven for a \lstinline|Monoid| is automatically applicable
to a \lstinline|Group|, a \lstinline|Ring|, or a \lstinline|Field|. Type class inference handles
this ``forgetful inheritance'' automatically. When a theorem requires a \lstinline|Monoid| but is
given a \lstinline|Ring|, Lean's type class synthesis systematically the hierarchy to
extract the underlying \lstinline|Monoid| structure.

Designing and maintaining this hierarchy is one of the most significant software engineering
achievements within the \textsf{mathlib} project. It ensures maximal theorem reuse, preventing
mathematicians from having to prove the same fundamental lemmas multiple times across different
domains of algebra.