\section{Definitions}

We choose to formalize formal group laws in Lean using Definition
\ref{Defn formal group}, since it is equivalent to the definitions in other references and
easier to check in practice.

The following is our definition of formal group laws in Lean:
\href{https://github.com/WenrongZou/FormalGroupLaws/blob/main/FormalGroupLaws/Basic.lean}{\faExternalLink}
\begin{lstlisting}
@[ext]
structure FormalGroup (R : Type*) [CommRing R] where
  toFun : MvPowerSeries (Fin 2) R
    /- Constant coefficient of `F` is zero. -/
    zero_constantCoeff : constantCoeff toFun = 0
    /- Coefficient of `X` and `Y` is 1. -/
    lin_coeff_X : coeff (single 0 1) toFun = 1
    lin_coeff_Y : coeff (single 1 1) toFun = 1
    /- Associativity condition: `F (F (X, Y), Z) = F (X, F (Y, Z))`.-/
    assoc : subst ![subst ![Y₀, Y₁] toFun, Y₂] toFun = subst ![Y₀, subst ![Y₁, Y₂] toFun] toFun (S := R)
\end{lstlisting}

In Mathlib, \lstinline{MvPowerSeries σ R} is the ring of multivariate power series with
indeterminates indexed by \lstinline{σ}. Also, \lstinline{Fin n} is a type with exactly
$n$ elements. To be specific, an element of \lstinline{Fin n} is an \lstinline{i : ℕ} together
with a proof \lstinline{i < n}. Moreover, \lstinline{MvPowerSeries.X (i : σ)} is the indeterminate
indexed by \lstinline{i}, and in the namespace \lstinline{MvPowerSeries} we can abbreviate
\lstinline{MvPowerSeries.X} as \lstinline{X}.
Therefore, \lstinline{X 0}, \lstinline{X 1}, and \lstinline{X 2} are the three indeterminates
in \lstinline{MvPowerSeries (Fin 3) R}. The notation \lstinline{Y₀, Y₁, Y₂} is an abbreviation
for \lstinline{X 0, X 1, X 2} in \lstinline{MvPowerSeries (Fin 3) R}. The expression
\lstinline{![a, b]} in the associativity condition is a map from \lstinline{Fin 2} to
\lstinline{α}, where \lstinline{a b : α}.
\lstinline{subst} is the function used to express substitution of (multivariate) power series.
For instance, $f(g(X_I))$ is expressed as \lstinline{f.subst g} and $F(f(X_I), g(X_I))$ is
expressed as \lstinline{F.subst ![f, g]}.
For the definition of commutative formal group laws, the only additional condition is commutativity.
\href{https://github.com/WenrongZou/FormalGroupLaws/blob/main/FormalGroupLaws/Basic.lean}{\faExternalLink}
\begin{lstlisting}
@[ext]
structure CommFormalGroup (R : Type*) [CommRing R] extends FormalGroup R where
/- Commutativity condition: `F(X,Y) = F(Y,X)`.-/
comm : toFun = subst ![X₁, X₀] toFun
\end{lstlisting}

Here, \lstinline{X₀, X₁} is an abbreviation for \lstinline{X 0, X 1} in \lstinline{MvPowerSeries (Fin 2) R}.

Mathematically, a commutative formal group is a formal group. In Lean, this statement is
expressed via coercions. An instance is as follows:

\begin{lstlisting}
/-- A commutative formal group law is a formal group law.-/
instance : Coe (CommFormalGroup R) (FormalGroup R) where
coe := CommFormalGroup.toFormalGroup
\end{lstlisting}

Another way to define a commutative formal group law is via the typeclass proposition
\lstinline|IsComm|.

\begin{lstlisting}
class IsComm (F : FormalGroup R) : Prop where
  comm : F.toFun = F.toFun.subst ![X₁, X₀]
\end{lstlisting}

In the early stages of this project, I chose the \lstinline|CommFormalGroup| definition.
However, using the \lstinline|IsComm| typeclass has proven to be more convenient in practice.

Given a formal group law, we can define a group structure on \lstinline{MvPowerSeries σ R}.
To be precise, let \lstinline{(F : FormalGroup R) (f₀ f₁ : MvPowerSeries σ R)}.
The sum of \lstinline{f₀} and \lstinline{f₁} is defined as \lstinline{subst ![f₀, f₁] F.toFun}.
In Lean, we can introduce the simpler notation

\begin{lstlisting}
abbrev add (F : FormalGroup R) (f g : MvPowerSeries σ R) : MvPowerSeries σ R := subst ![f, g] F.toFun
\end{lstlisting}

In the environment of \lstinline{namespace FormalGroup}, \lstinline{+[F]} denotes addition with respect to \lstinline{F : FormalGroup R}. More specifically, given two multivariate power series $f, g \in R[\![X_I]\!]$, where $I$ is an index set, and assuming the constant coefficients of $f$ and $g$ are zero,
\lstinline{f +[F] g} means $F(f,g)$.

With this notation, we can rewrite the associativity condition and the commutativity
condition in the \lstinline{namespace FormalGroup} as follows:
\begin{lstlisting}
/-- The addition under the sense of formal group `F` is associative. -/
theorem add_assoc {F : FormalGroup R} {Z₀ Z₁ Z₂ : MvPowerSeries σ R} (hZ₀ : constantCoeff Z₀ = 0) (hZ₁ : constantCoeff Z₁ = 0) (hZ₂ : constantCoeff Z₂ = 0):
Z₀ +[F] Z₁ +[F] Z₂ = Z₀ +[F] (Z₁ +[F] Z₂) := ...
\end{lstlisting}

\begin{lstlisting}
theorem add_comm {F : FormalGroup R} [hF : F.IsComm] {Z₀ Z₁ : MvPowerSeries σ R}
(hZ₀ : constantCoeff Z₀ = 0) (hZ₁ : constantCoeff Z₁ = 0):
  Z₀ +[F] Z₁ = Z₁ +[F] Z₀ := ...
\end{lstlisting}

To show that the formal addition defined by a formal group law $F$ forms an
additive group, we should verify that there is a unit for this addition, namely
$F(X,0)=X$ and $F(0,Y)=Y$. Furthermore, we should prove that there exists a unique additive
inverse element. \par

The existence of an additive unit in the sense of $F$ is formalized by the following two theorems.
\begin{lstlisting}
theorem zero_left : subst ![0, PowerSeries.X] F.toFun = PowerSeries.X (R := R) := ...

theorem zero_right : subst ![PowerSeries.X, 0] F.toFun = PowerSeries.X (R := R) := ...
\end{lstlisting}

Using the same notation for formal group addition, we can generalize the above theorems to
the following two theorems.

\begin{lstlisting}
theorem zero_add (h : constantCoeff f = 0) : 0 +[F] f = f :=

theorem add_zero (h : constantCoeff f = 0) : f +[F] 0 = f :=
\end{lstlisting}

Here, the name \lstinline{zero_add} means that adding zero to a multivariate power series
\lstinline{f} gives \lstinline{f} itself, which is a standard naming convention in Mathlib.
To distinguish this theorem from other theorems with the same name, we place it in the
\lstinline{namespace FormalGroup}.

Now we discuss the construction of the additive inverse of a formal group law.

\begin{lstlisting}
abbrev addInv_aux (F : FormalGroup R) : ℕ → R
  | 0 => 0
  | 1 => -1
  | n + 1 => - (coeff (n + 1) (F.toFun.subst
    ![X, (∑ i : Fin (n + 1), C (addInv_aux F i.1) * X ^ i.1)]))

def addInv_X : PowerSeries R := .mk (addInv_aux F ·)

def addInv (φ : MvPowerSeries σ R) : MvPowerSeries σ R := subst φ (addInv_X F)
\end{lstlisting}

The API \lstinline|addInv_X| is the additive inverse of \lstinline|X| with respect to the formal group
law \lstinline|F|. For an arbitrary multivariate power series, \lstinline|addInv φ| is the additive
inverse of \lstinline|φ|. Via direct calculation and induction, we have the theorem

\begin{lstlisting}
theorem subst_addInv_eq_zero : F.toFun.subst ![X, (addInv_X F)] = 0 := by
\end{lstlisting}

\subsection{Examples of formal groups}

The basic examples of formal group laws are the additive formal group law $\bfG_a$ and the multiplicative formal group law $\bfG_m$. We formalize them using our definition of \lstinline{FormalGroup R}.
\begin{lstlisting}
def Gₐ : FormalGroup R where
  toFun := X₀ + X₁
  ...

instance : (Gₐ (R := R)).IsComm where ...

def Gₘ : FormalGroup R where
  toFun := X₀ + X₁ + X₀ * X₁
  ...

instance : (Gₘ (R := R)).IsComm where ...
\end{lstlisting}

\subsection{Functions Between Formal Groups}

According to \ref{defn: pushforward of coeff ring}, given two commutative rings $R$ and $R'$, a ring
homomorphism $\phi : R \to R'$, and a formal group law $F$ over $R$, then $\phi_* F$ is a formal
group law over $R'$. The construction of the pushforward on the coefficient ring in Lean
is: \href{https://github.com/WenrongZou/FormalGroupLaws/blob/main/FormalGroupLaws/Basic.lean}{\faExternalLink}

\begin{lstlisting}
def map {R : Type*} [CommRing R] {R' : Type*} [CommRing R']
    (f : R →+* R') (F : FormalGroup R): FormalGroup R' where
  toFun := F.toFun.map f
  ...
\end{lstlisting}

Let $R$ be a commutative ring and $T$ be a subring of $R$. Given a (multivariate) power series
$f$ over $R$ with the assumption that all coefficients of $f$ are in the subring $T$, $f$ can
be considered as a (multivariate) power series over $T$. We define this function as
\lstinline{MvPowerSeries.toSubring}, following the APIs for polynomials as inspiration.

\begin{lstlisting}
variable [Ring R] (p : MvPowerSeries σ R) (T : Subring R) (hp : ∀ n, p.coeff n ∈ T)

def MvPowerSeries.toSubring : MvPowerSeries σ T := fun n => ⟨p.coeff n, hp n⟩
\end{lstlisting}

According to the definition, their coefficients should be the same after coercion. The
\lstinline{@[simp]} tag in the following theorem means that this theorem can be applied
automatically when we use the tactic \lstinline{simp} to simplify an expression.

\begin{lstlisting}
@[simp]
theorem coeff_toSubring {n : σ →₀ ℕ} : (p.toSubring T hp).coeff n = p.coeff n := rfl
\end{lstlisting}

Given a formal group law $F$ over a ring $R$ with the assumption that all coefficients of $F$
are in the subring $T$, then $F$ is a formal group law over $T$.

\begin{lstlisting}
def FormalGroup.toSubring (F : FormalGroup R) (hF : ∀ n, F.toFun n ∈ T) : FormalGroup T where
  toFun := F.toFun.toSubring _ hF
  ...
\end{lstlisting}

Similarly, we can define \lstinline{FormalGroup.toSubring_comm}, which says that
the commutativity condition is preserved under the \lstinline|toSubring| map.

\begin{lstlisting}
lemma FormalGroup.toSubring_comm (F : FormalGroup R) (hF : ∀ n, F.toFun n ∈ T) :
    F.toFun.toSubring _ hF = (F.toFun.toSubring _ hF).subst ![X₁, X₀] := ...

lemma FormalGroup.toSubring_IsComm (F : FormalGroup R) [F.IsComm]
    (hF : ∀ n, F.toFun n ∈ T) :
    (F.toSubring _ hF).IsComm := ...
\end{lstlisting}

\subsection{Homomorphism and Isomorphism}

First, we need the API \lstinline{PowerSeries.toMvPowerSeries}, which is inspired by a
similar API for polynomials.

\begin{lstlisting}
noncomputable
def Polynomial.toMvPolynomial (i : σ) : R[X] →ₐ[R] MvPolynomial σ R :=
  aeval (MvPolynomial.X i)
\end{lstlisting}
Given a power series $p(X) \in R[\![X]\!]$ and an index $i \in I$ where $I$ is an index set,
this is a function that maps $p(X)$ to $p(X_i) \in R[\![X_I]\!]$.

\begin{lstlisting}
def PowerSeries.toMvPowerSeries (f : PowerSeries R) (i : σ) : MvPowerSeries σ R :=
  f.subst (MvPowerSeries.X i)
\end{lstlisting}

For the definition of a homomorphism in \ref{defn: hom of formal group law} between two formal
group laws, we use a \lstinline{structure} in Lean:
\href{https://github.com/WenrongZou/FormalGroupLaws/blob/main/FormalGroupLaws/Basic.lean#L856-L863}{\faExternalLink}
\begin{lstlisting}
@[ext]
structure FormalGroupHom  (G₁ G₂ : FormalGroup R) where
  toFun : PowerSeries R
  zero_constantCoeff : toFun.constantCoeff = 0
  hom : toFun.subst (G₁.toFun) = G₂.toFun.subst (R := R) toFun.toMvPowerSeries
\end{lstlisting}

Since two formal group homomorphisms are the same if and only if their underlying
functions are the same, we add a tag \lstinline{@[ext]} to the structure. When \lstinline{@[ext]}
is applied to a structure, it generates an \lstinline{.ext} theorem and applies the
\lstinline{@[ext]} attribute to it. The result is an \lstinline{.ext} and an \lstinline{.ext_iff}
theorem with the \lstinline{.ext} theorem registered for the \lstinline{ext} tactic.

An isomorphism between two formal groups is defined as a pair of formal group homomorphisms
that are inverses of each other.

\begin{lstlisting}
@[ext]
structure FormalGroupIso (G₁ G₂ : FormalGroup R) where
  toHom : FormalGroupHom G₁ G₂
  invHom : FormalGroupHom G₂ G₁
  left_inv : (PowerSeries.subst toHom.toFun) ∘ (PowerSeries.subst invHom.toFun) = id
  right_inv : (PowerSeries.subst invHom.toFun) ∘ (PowerSeries.subst toHom.toFun) = id
\end{lstlisting}

Here we also add the tag \lstinline{@[ext]} to \lstinline{structure FormalGroupIso}, and
we automatically obtain the theorem

\begin{lstlisting}
variable {G₁ G₂ : FormalGroup R} {x y : FormalGroupIso G₁ G₂}

theorem FormalGroupIso.ext_iff :
    x = y ↔ x.toHom = y.toHom ∧ x.invHom = y.invHom := ...
\end{lstlisting}

To show that two formal group isomorphisms are the same, it is enough to show that their
\lstinline{toHom} is the same. Indeed, if we have \lstinline{x.toHom = y.toHom}, then
\lstinline{x.invHom = y.invHom} is also true, since \lstinline{invHom} is the substitution
inverse of \lstinline{toHom} and the substitution inverse is unique. The following theorem
is more convenient to use in practice.

\begin{lstlisting}
theorem FormalGroupIso.ext_iff' : x = y ↔ x.toHom = y.toHom := ...
\end{lstlisting}

Let $F(X,Y), G(X,Y)$ be formal group laws over a ring $R$. A homomorphism of formal group
laws $\alpha(X)$ from $F(X,Y)$ to $G(X,Y)$ is an isomorphism if and only if
the coefficient of $X$ in $\alpha(X)$ is invertible in $R$.

\begin{lstlisting}
theorem isIso_of_isUnit_coeff_one {G₁ G₂ : FormalGroup R} (α : FormalGroupHom G₁ G₂)
    (h : IsUnit (α.toFun.coeff 1)) :
    ∃ (α₁ : FormalGroupIso G₁ G₂), α₁.toHom = α := by

theorem isUnit_coeff_one_of_isIso {G₁ G₂ : FormalGroup R} (α : FormalGroupIso G₁ G₂) :
    IsUnit (α.toHom.toFun.coeff 1) := by
\end{lstlisting}

There are two ways to express an element \lstinline|a| of a ring \lstinline|R| to be invertible. The
first one is \lstinline|IsUnit a|, while the second one is \lstinline|Invertible a|.
I briefly explain their difference.

The type \lstinline|IsUnit a| is defined as a \lstinline|Prop| (a proposition). Under the hood,
it asserts that there exists some unit $u$ in the group of units $R^\times$ such that $u$, when coerced
to $R$, equals $a$. It merely states the fact that an inverse exists. It tells Lean's typechecker,
``I promise an inverse exists somewhere.'' A limitation is that, since it is a
\lstinline|Prop|, it is subject to proof irrelevance. Lean erases propositions during computation.
One cannot easily extract the inverse from \lstinline|IsUnit a| to use in a computable function
without invoking the Axiom of Choice (which makes the resulting definition
\lstinline|noncomputable|).

Conversely, \lstinline|Invertible a| is a typeclass (residing in \lstinline|Type|)
that explicitly packages the element $a$ with its concrete inverse. It conceptually contains
the inverse element itself, alongside the proofs that multiplying them together yields
$1$ in the ring. It provides explicit, computable access to the inverse. Because it is a typeclass,
Lean's typeclass synthesis system can automatically find and apply inverses. Also, having an
\lstinline|[Invertible a]| instance in the local context allows the use of the special notation
to write the inverse of $a$ directly in algebraic expressions.

\begin{lstlisting}
theorem isUnit_of_invertible [Monoid α] (a : α) [Invertible a] : IsUnit a :=
\end{lstlisting}

The theorem \lstinline|isUnit_of_invertible| in Mathlib gives one direction of the
equivalence between these two notions.

In the proof of these two theorems, we need the result that, given a power series $f(X)$
over a ring $R$, if the coefficient of $X$ in $f(X)$ is invertible and the constant coefficient
is zero, then there exists a power series $g(X)$ over $R$ such that $f(g(X)) = g(f(X)) = X$.

\begin{lstlisting}
variable (P : PowerSeries R) (hP : P.constantCoeff = 0) [Invertible (coeff 1 P)]

noncomputable
def substInvFun : ℕ → R
  | 0 => 0
  | 1 => 1 / (coeff _ 1 P)
  | n + 1 => - 1 / (coeff 1 P) *
      (coeff (n + 1) (P.subst (∑ i : Fin (n + 1), C (substInvFun i.1) * X ^ i.1)))
\end{lstlisting}

From the construction and computation, we obtain the following theorem:

\begin{lstlisting}
lemma substInv_subst : P.substInv.subst P = X :=
\end{lstlisting}

Also, we can prove that this substitution inverse is unique.